### 2014-11-26 ThesisJo/derivations.tex
la2pdf commit - 2014:11:24	14:53:56	(Mon24.Nov)
la2pdf commit - 2014:11:24	17:42:43	(Mon24.Nov)
la2pdf commit - 2014:11:24	18:32:43	(Mon24.Nov)
la2pdf commit - 2014:11:24	19:08:58	(Mon24.Nov)
la2pdf commit - 2014:11:26	19:01:05	(on.26.nov.)

>>>>

\section{LCA tricks}

Let $\x$ be the data received by an array, pre-steered to some pixel in the image, and $\w$ be the window applied to these spatial data. Then we defined the beamformer outout $z$ as the weighted sum of the data:
%
\begin{align}
z(\w,\x) = \w\H\x = \sumb{m=0}{M-1} w_m x_m^*
\end{align}
%
Now let us choose a trigonometric window function:
%
\begin{align}
\w = \frac{e^{j\varphi}}{2\pi\alpha}\big(\alpha + (1-\alpha)\cos\left(\frac{2\pi n}{N-1}\right)\big)
\end{align}
%
Inserting this yields:
%
\begin{align}
\w\H\x &= \sumb{m=0}{M-1} e^{j\varphi}\Big(\alpha + (1-\alpha)\cos\theta\Big) x_m^* \nn
&= \sumb{m=0}{M-1} e^{j\varphi}\Big(\alpha + (1-\alpha)\cos\theta\Big) x_m^*
\end{align}
%
where $\theta = \frac{2\pi n}{N-1}$.

LCA can then be defined as
%
\begin{align}
\argmin{\w}\ |z|^2 = \argmin{\w}\ z\,z^* = %\argmin{\w}\ \w\H\x = \sumb{m=0}{M-1} w_m^* x_m
\end{align}

\newpage
\section{MVDR}

By definition, the beamformer output $z[n]$ can now be expressed as the weighted sum of all the delayed data samples:
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{z}
\end{align}
where $w_m$ is the weight factor assigned to channel $m$. With static weights this would be referred to as the conventional delay-and-sum (DAS) beamformer. A large variety of weighting functions exists here for trading lateral resolution for improved noise suppression (contrast), but one always ends up with a compromise between the two~\cite{Harris1978}.

Various adaptive beamformers target this limitation by allowing the weights to change for each pixel to better fit the dynamic nature of the incoming wavefield. In other words, they attempt to use the \emph{a priori} information present in the data to improve image quality. The MVDR beamformer is one such method. It finds the set of complex weights that minimizes the beamformer's expected output power, while ensuring unity gain in the look direction~\cite{Capon1969}. This is a convex optimization problem that can be solved using Lagrange multipliers to yield the solution
\begin{gather}
\vec w[n] = \frac{\Ri[n]\a}{\a\T\Ri[n]\a},\label{weights}
\end{gather}
where $\a$ is a steering vector and $\R=E\{\x[n]\x\H[n]\}\in\mathbb{C}^{M,M}$ is the spatial covariance matrix for the full array. Since we pre-steer our data to every pixel in the image we simplify (\ref{weights}) by substituting $\a$ with a row vector $\1$ that represents broadside phase-steering. To estimate $\R$ we compute a sample covariance matrix $\eR$. In this computation we perform some degree of:
\begin{itemize}
\item \emph{spatial averaging} to avoid signal cancellation by decorrelating coherent echoes~\cite{Kailath1985};
\item \emph{temporal averaging} over an interval comparable to the pulse length (one to five samples) to maintain true speckle statistics~\cite{Synnevag2009a};
\item \emph{diagonal loading} to improve robustness to parameter errors~\cite{Cox1987,Maksym1979}.
\end{itemize}%
